An efficient contact value approach to approximating the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-07-07 papers/pair-correlation/paper.tex
plot just the nice values of ff, but fit to all of them. Tested on darcy. Took 0:40.89.

\begin{table}
  \begin{align*}
    \kappa &= \kappatable
  \end{align*}
  \caption{The fitted $\kappa_{ij}$ matrix.  In addition to these 12
    parameters, we also optimized the exponetial decay constant
    $\alpha=\alphaval$.
    %% Note that the first column of $\kappa$ corresponds to $j=1$
    %% while the first row corresponds to $i=1$ in
    %% Eq.~\ref{eq:fit-form}.
  }
\end{table}

The Gil-Villegas function is fit to data for $r <= \maxrfit R$.  The
maximum error within this radius in $g_S(r)$ at packing fractions up
to 0.4 is \maxerr, which occurs at $\eta = \etamaxerr$ and $r =
\rmaxerr R$.

>>>>

\begin{table}
  \begin{align*}
    \kappa &= \kappatable
  \end{align*}
  \caption{The fitted $\kappa_{ij}$ matrix.
    %% In addition to these 12 parameters, we also optimized the
    %% exponetial decay constant $\alpha=\alphaval$.za
    %% Note that the first column of $\kappa$ corresponds to $j=1$
    %% while the first row corresponds to $i=1$ in
    %% Eq.~\ref{eq:fit-form}.
  }
\end{table}

The Gil-Villegas function is fit to data for $r <= \maxrfit R$.  The
maximum error within this radius in $g_S(r)$ at packing fractions up
to 0.45 is \maxerr, which occurs at $\eta = \etamaxerr$ and $r =
\rmaxerr R$.  We used in this fit Monte Carlo data for the radial
distribution function at values of packing fraction at increments of
0.05 from 0.05 to 0.45. Fig.~\ref{fig:radial-distribution} displays
our approximation at just under half of the densities that were
included in the fit.
